\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style

\section{Qualitative Testing}
\label{sec:qualitative}
We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and identify stumbling points in the interface.
At the completion of the task, we interviewed our participants to gather explanatory data and their opinions.

@@

\subsection{Procedure} 
We ran the experiments in a small room with a desk and chair, where a monitor, keyboard, and a Windows computer were set up. Using a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment. We ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen before each participant.

>>>>

\section{Qualitative Testing}
\label{sec:qualitative}
We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and identify stumbling points in the interface.
We interviewed our participants to gather explanatory data and their opinions.

@@

\subsection{Procedure} 
We ran the experiments in a small room where a monitor, keyboard, and a Windows computer were set up. Using a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment. Before each participant, we ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
